### 2020-09-13 paper/experiments.tex
plots
Plot detailed almost done

Let us describe experiments and their results. All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one. Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/perf.t.in.out.csv.lines.pgf}
    \caption{Random perfect graphs}
    \label{plot:perfLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/perf.t.in.out.csv.detailed.pgf}
    \caption{Random perfect graphs}
    \label{plot:perfDet}
  \end{subfigure}
  \caption{Random perfect graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/perf2.t.in.out.csv.lines.pgf}
    \caption{Line graphs of random bipartite graphs}
    \label{plot:perf2Lines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/perf2.t.in.out.csv.detailed.pgf}
    \caption{Line graphs of random bipartite graphs}
    \label{plot:perf2Det}
  \end{subfigure}
  \caption{Line graphs of random bipartite graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
    \caption{Overall running times}
    \label{plot:gridLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/grid6by5to11.t.in.out.csv.detailed.pgf}
    \caption{Percentage of time taken be each part}
    \label{plot:gridDet}
  \end{subfigure}
  \caption{Lattice graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
    \caption{Overall running times}
    \label{plot:rookLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/rookGraph5by4to7.t.in.out.csv.detailed.pgf}
    \caption{Percentage of time taken be each part}
    \label{plot:rookDet}
  \end{subfigure}
  \caption{Rook graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
    \caption{Overall running times}
    \label{plot:knightLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
    \caption{Percentage of time taken be each part}
    \label{plot:knightDet}
  \end{subfigure}
  \caption{Knight graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
    \caption{Overall running times}
    \label{plot:hypercubeLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
    \caption{Percentage of time taken be each part}
    \label{plot:hypercubeDet}
  \end{subfigure}
  \caption{Hypercube graphs}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/split20to50.t.in.out.csv.lines.pgf}
    \caption{Overall running times}
    \label{plot:splitLines}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \input{plots/split20to50.t.in.out.csv.detailed.pgf}
    \caption{Percentage of time taken be each part}
    \label{plot:splitDet}
  \end{subfigure}
  \caption{Split graphs}
\end{figure}

>>>>

Let us describe experiments and their results. All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one. Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks. For every test, the vertex number were shuffled.

@@

\begin{figure}
  \centering
  \input{plots/perf.t.in.out.csv.lines.pgf}
  \label{plot:perfLines}
  \caption{Random perfect graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/perf2.t.in.out.csv.lines.pgf}
  \label{plot:perf2Lines}
  \caption{Line graphs of random bipartite graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
  \label{plot:gridLines}
  \caption{Lattice graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
  \label{plot:rookLines}
  \caption{Rook graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
  \label{plot:knightLines}
  \caption{Knight graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
  \label{plot:hypercubeLines}
  \caption{Hypercube graphs}
\end{figure}

@@

\begin{figure}
  \centering
  \input{plots/split20to50.t.in.out.csv.lines.pgf}
  \label{plot:splitLines}
  \caption{Split graphs}
\end{figure}

\begin{figure}
  \centering
  \input{plots/detailed.csv.detailed.pgf}
  \label{plot:splitLines}
  \caption{\the\textwidth \the\textheight}
\end{figure}
